Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-10-24 cbm-rbd-paper.tex
RBD figure, surv sign table

We consider a system with components of $k=1,\ldots,K$ different types;
for each type $k$, there are $N_k$ exchangeable components in the system.

***example reliability block diagram

component model: weibull with fixed shape,
inverse gamma prior on scale parameter,
fix priors via expected lifetime and prior strength,

test data inclusion
with noninformatiove right-censoring

RUL/RLD via survival signature,
posterior predictive distributions,
system reliability distribution (RUL/RLD) as output,

output is the current system reliability curve
taking into account the current system state,
including the current ages of system components, 
and the lifetime histories of all component types,
including test data and expert assessments.

***RUL model description below follows closely \cite{2016:walter-coolen},
which describes the same RUL/RLD model.
However, \cite{2016:walter-coolen} does not consider maintenance policies,
and focuses instead on a generalization of the RUL/RLD model using sets of priors for the component models
(which can be seen as parametric P-boxes),
allowing for vague and partial prior specifications,
and sensitivity to prior-data conflict \cite[\S 2.2.3.3]{diss}.

@@

@@

Here we describe how system reliability functions, given fixed component models,
can be efficiently calculated using the survival signature.
We will show in Section~***
how this method can be used to find the system reliability function $\Rsysnow(t)$ at current time $\tnow$ for a monitored system,
giving us the RUL/RLD distribution on which we base our adaptive maintenance policy.

We consider systems of arbitrary reliability block diagram layout,
consisting of components of $K$ different types,
where there are $N_k$ components of type $k$ in the system,
and the total number of components in the system is $\sum_{k=1}^K N_k = N$.
An example system reliability block diagram is given in Figure~***.
Note that this system cannot be described as a nesting of series and parallel subsystems.
%This system is observed until time $\tnow$,
%leading to censored observation of certain component lifetimes within the system.

@@

***An example for the survival signature for the system in Figure *** is given in Table ****.

@@

\subsection{System reliability function at $\tnow$}

>>>>

***component model: weibull with fixed shape,
inverse gamma prior on scale parameter,
fix priors via expected lifetime and prior strength,
test data inclusion
with noninformatiove right-censoring

***RUL/RLD via survival signature,
posterior predictive distributions,
system reliability distribution (RUL/RLD) as output,

***output is $\Rsysnow(t)$, the current (at time $\tnow$) system reliability function
(residual life distribution, RLD)
taking into account the current system state,
including the current ages of system components, 
and the lifetime histories of all component types,
including test data (if available) and expert assessments.

We can analyze systems of arbitrary layout, consisting of components of $k=1,\ldots,K$ different types,
where for each type $k$, there are $N_k$ exchangeable components in the system.
As an example, Figure~\ref{fig:bridge-layout} depicts the reliability block diagram of a bridge type system
with three component types $A$, $B$, $C$, where $N_A=4$, $N_B=1$, and $N_C=1$.

***Model description in this Section follows closely \cite{2016:walter-coolen},
who present the same RUL/RLD model.
However, \cite{2016:walter-coolen} do not consider maintenance policies,
and focus instead on a generalization of the RUL/RLD model using sets of priors for the component models
(which can be seen as parametric P-boxes),
allowing for vague and partial prior specifications,
and sensitivity to prior-data conflict \cite[\S 2.2.3.3]{diss}.

\begin{figure}
\centering
\begin{tikzpicture}
[type1/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
 type2/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
 type3/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
 cross/.style={cross out,draw=red,very thick,minimum width=7mm, minimum height=5mm},
 hv path/.style={very thick, to path={-| (\tikztotarget)}},
 vh path/.style={very thick, to path={|- (\tikztotarget)}}]
%\begin{scope}[scale=0.75]
\node[type1] (T1-2) at ( 1.4, 1) {$A_1$};
\node[type1] (T1-3) at ( 1.4,-1) {$A_2$};
\node[type1] (T1-5) at ( 4.2, 1) {$A_3$};
\node[type1] (T1-6) at ( 4.2,-1) {$A_4$};
\node[type2] (T2)   at ( 2.8, 0) {$B_1$};
\node[type3] (T3)   at ( 5.6, 0) {$C_1$};
\coordinate (start) at (0  ,0);
\coordinate (end)   at (6.3,0);
\coordinate (bista) at (0.7,0);
\coordinate (biend) at (4.9,0);
\path (bista)     edge[hv path] (start)
                  edge[vh path] (T1-2.west)
                  edge[vh path] (T1-3.west)
      (T1-2.east) edge[hv path] (T2.north)
      (T1-3.east) edge[hv path] (T2.south)
      (T2.north)  edge[vh path] (T1-5.west)
      (T2.south)  edge[vh path] (T1-6.west)
      (biend)     edge[vh path] (T1-5.east)
                  edge[vh path] (T1-6.east)
                  edge[hv path] (T3.west)
      (T3.east)   edge[hv path] (end);
%\end{scope}
\end{tikzpicture}
\caption{Reliability block diagram for a `bridge' type system with three component types $A$, $B$, $C$.
Note that this system layout cannot be expressed as a nesting of series and parallel layouts.
The corresponding survival signature $\Phi(l_A,l_B,l_C)$ is given in Table~\ref{tab:bridge-survsign}.}
\label{fig:bridge-layout}
\end{figure}

@@

\begin{table}
\centering
\begin{tabular}{ccclccccl}
  \toprule
$l_A$ & $l_B$ & $l_C$ & $\Phi$ & \quad & $l_A$ & $l_B$ & $l_C$ & $\Phi$\\ 
  \midrule
0 & 0 & 1 & 0    & & 0 & 1 & 1 & 0 \\ 
1 & 0 & 1 & 0    & & 1 & 1 & 1 & 0 \\ 
2 & 0 & 1 & 0.33 & & 2 & 1 & 1 & 0.67 \\ 
3 & 0 & 1 & 1    & & 3 & 1 & 1 & 1 \\ 
4 & 0 & 1 & 1    & & 4 & 1 & 1 & 1 \\ 
   \bottomrule
\end{tabular}
\caption{Survival signature $\Phi(l_A,l_B,l_C)$ for the bridge system from Figure~\ref{fig:bridge-layout},
omitting all rows with $l_C=0$, since $\Phi(l_A,l_B,0)=0$ for all $l_A$ and $l_B$.}
\label{tab:bridge-survsign}
\end{table}

@@

Here we describe how system reliability functions, given fixed component models,
can be efficiently calculated using the survival signature.
We will show in Section~\ref{sec:sysreltnow}
how this method can be used to find the system reliability function $\Rsysnow(t)$ at current time $\tnow$ for a monitored system,
giving us the RUL/RLD distribution on which we base our adaptive maintenance policy.

We consider systems of arbitrary reliability block diagram layout,
consisting of components of $K$ different types,
where there are $N_k$ components of type $k$ in the system,
and the total number of components in the system is $\sum_{k=1}^K N_k = N$.
An example system reliability block diagram is given in Figure~\ref{fig:bridge-layout}.
Note that this system cannot be described as a nesting of series and parallel subsystems.
%This system is observed until time $\tnow$,
%leading to censored observation of certain component lifetimes within the system.

@@

As an example, the survival signature for the system in Figure~\ref{fig:bridge-layout} is given in Table~\ref{tab:bridge-survsign}.

@@

\subsection{System reliability function at $\tnow$}
\label{sec:sysreltnow}
